Enforced Invariant Confluence

### 2018-04-18 doc/paper/sections/evaluation.tex
Finished benchmark part of eval.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{figures/vary_nodes.pdf}
  \caption{}\figlabel{}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\columnwidth]{figures/vary_nodes.pdf}
  \caption{%
    Throughput of eventually consistent, segmented invariant-confluent, and
    linearizable replication measured against the number of
    nodes.
  }\figlabel{VaryNodes}
\end{figure}

\begin{benchmark}
  In this benchmark, we measure the scale-out of segmented invariant-confluent
  replication. We repeat \benchref{VaryWithdraws} with a 10\% withdrawal rate,
  but this time we vary the number of servers we use to replicate our object.
  When we replicate with $n$ servers, we use $3n$ clients (the $3$ colocated
  clients on each server) as part of the workload. The results are shown in
  \figref{VaryNodes}.

  Eventually consistent replication scales perfectly with the number of nodes,
  confirming the results in~\cite{bailis2014coordination}. With eventually
  consistent replication, servers do not coordinate at all, so they are
  completely unaffected by the number of servers. Linearizable replication, on
  the other hand, scales up to about 3-5 servers before performance begins to
  decrease. These numbers are consistent with typical deployments of
  state-machine replication protocols like Paxos~\cite{chandra2007paxos}.
  Because all messages are sent to the leader, the leader becomes the
  bottleneck as the number of servers and clients increases. Moreover, the
  leader must wait for responses from more servers, increasing the latency of
  the slowest response which in turn decreases throughput.
  Segmented invariant-confluent replication scales up to about 6-8 servers
  before succumbing to the same scalability bottlenecks as linearizable
  replication.

  These results highlight the importance of coordination avoidance in
  distributed databases. While segmented invariant-confluent replication scales
  out slightly better than linearizable replication, both scale significantly
  worse than eventually consistent replication even for a very low (i.e.\ 10\%)
  withdrawal workload. This demonstrates that even a small amount of
  coordination can significantly reduce the scalability of a system.
\end{benchmark}
